CFTP Convergence

### 2024-12-09 extensive_tests/CFTP_convergence/draft-test_CFTP_convergence.Rmd
Adding files for test CFTP convergence workflow for reproducibility

---
title: "ABC inferences"
output: 
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Introduction to MethEvolSIM}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

- R packages: optparse (add to dependencies), parallel, ape

@@

- An .RData file with a tree in ape format (TODO: modify this and check whether scrm is also producing trees in the same format)

@@

1. Save as simulation design the genomic structure, tree(s) -- GIVEN -- and sampled parameter combinations.

2. Run the simulations. TODO: Before submitting load package without devtools

3. Compute the selected summary statistics. TODO: When added sumStats functions to package, stop sourcing script.

4. Assess ABC accuracy using cross-validation.

5. Infer parameters from empirical DNA methylation data.

>>>>

---
title: "CFTP Convergence"
output: 
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Test for CFTP Convergence}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

- R packages:

@@

@@

1. Bla

### Scripts

- `run_sim.R`. TODO: Update way in which the package is loaded before submitting.
